---
title: "Toon's music visualisations"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

# Introduction
### Welcome to my page!!!
#### Why I chose this course
As a third year AI bachelor student I already encountered two courses about music and the role of AI or atleast computers in interpreting music. For my 'tweedejaarsproject' I worked with a dataset of the Eurovision Song Festival. When I was younger, music (in physics) was my least favourite subject, but the more I learned about it, the more I came to love it.

#### My corpus
I would like to find out how The Beach Boys evolved over the years [placeholder]
###### Motivation
I listen to music a lot (not very special), but I found that I listen to old music more often than the average person of my age. 
###### Challenges
[Placeholder]
#### Spotify API
I have already used python musical modules like <em>Essentia</em> and I really enjoyed the technical part of music, so I am looking forward using the <em>Spotify API</em>.

# Visualisation
```{r}
library(tidyverse)
library(spotifyr)
bb <- get_artist_audio_features('the beach boys')
good_vibrations <- 
  bb %>% 
    filter(track_id=='6aU6a9tdn2vHhnPGlboFZX')

```



```{r}
ggplot(bb,aes(x=energy,y=valence)) +
  geom_point()

```

# Discussion
